---
title: "Bulk processing"
author: "Fonti Kar"
date: "2024-01-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install/Load packages
# install.packages("pacman")
pacman::p_load(readxl, dplyr, purrr, lubridate, stringr, readr)

# Load functions 
source("R/clean_data.R")
source("R/guess.R")
source("R/menu.R")
```

### Locate folder

This code will list all the files out in the folder and create relative paths for each.

Tip: If your files are not in this project folder, `"~/"` will take you to the root of your computer folders. From there, use the Tab key to look and navigate to the folder that holds your file

```{r}
# Folder containing data
path <- "data/"

# List all the files inside the folder
file.path(path, list.files(path))

# Assign these file names into an object
raw_files_paths <- file.path(path, list.files(path))
```


### Reformat data

```{r}

```

### Identifying/Guessing blanks

```{r}

```

### Renaming blanks

```{r}

```

### Renaming subject lanes

```{r}

```

### Saving output