---
title: "Bulk processing"
author: "Fonti Kar"
date: "2024-01-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

# Install/Load packages
# install.packages("pacman")
pacman::p_load(readxl, dplyr, purrr, lubridate, stringr, readr, here)

# Load functions 
source(here("R/clean_data.R"))
source(here("R/guess.R"))
source(here("R/menu.R"))
```

### Locate file and reformat data

Please provide the relative path to the file of the SDR output.

The `file.choose()` function allows you to choose the file you want to clean. 

The `reformat_sdr()` function calls several sub-functions to clean the raw data:

1. `remove_header()`, to remove the top part of the output file
2. `remove_additional_sensor_columns()`, to remove the extra columns on the right side of the output file 
3. `remove_No_Sensor()`, to remove rows where no sensory was detected by the SDR
4. `create_elapsed_time()`, to rename `Time/Min` column to `elapsed_time`
5. `create_date_time_cols()`, to create separate columns for date and time of measurement
6. `change_data_formats()`, to set the `date` as a date variable and the `elapsed_time` and each lane's data as numeric variables. 

 Remember to assign the output to an object!

```{r}
# Choose your file
file <- file.choose()

# Reformat file and assign to data
data <- reformat_sdr(file)

# Look at data
data
```


### Identifying/Guessing blanks

Next we will identify the blank or empty lanes with the`guess_blanks()` function. The idea behind this function is to take the lanes that have an average air saturation over a particular `threshold`. 

To illustrate, lets calculate the average air saturation for all lanes:

```{r}
data |> 
  select(A1:D6) |> # Select the lanes
  colMeans() |> # Compute means for each column
  round(2) # Round to 2 decimal places
```
 
Now let's try it out the `guess_blanks()` function. By default, the threshold is set at `90`. You will have to adjust this for lower temperatures or very tiny organisms. Remember to assign the output to an object!

```{r}
blank_lanes <- guess_blanks(data, threshold = 90)
blank_lanes
```

If `guess_blanks` is not working well, you can also manually enter the ID of the blanks in the next step

### Renaming blanks

Next we will rename the blank lanes by adding a prefix to their lane IDs. By default the prefix is `control`, you can change this with the `replace_name` argument. The blanks are renamed sequentially according the order of input. 

Here we are using the `blank_lanes` identified by the previous function for renaming. Remember to assign the output to an object!

```{r}
renamed_blanks <- data |> 
  rename_blanks(all_of(blank_lanes))

renamed_blanks
```

Alternatively, you can manually type in the ID of the blank lanes. Here we are also changing the prefix to `blank_` as well. *Note, no quotes about each ID. 

```{r}
data |> 
  rename_blanks(c(D1, D2, D3, D4, D5, D6), replace_name = "blank") |> 
  names() 
```

### Assigning IDs to subject lanes

Now we can proceed to renaming the lanes that contained actual subjects with the `assign_subj_ids()` function. The function will bring up an empty "key" where the default lane ID is in column `subj`. You will be populating the adjacent column `true_id`. 

**Remember to assign the output of the function to an object, otherwise your progress will not be saved!**

The function `assign_subj_ids()` will bring up an interactive menu in the console. There are three options to choose from in the top menu: 

1. Assign ID to lane
2. Quit
3. Update column names

Type the number next to the desired option to make the selection

```{r}
naming_lanes <- assign_subj_ids(renamed_blanks)
```

#### Renaming lane IDs

Selecting option 1, will bring up all your all the subject lanes in your data. Each will have a number next to the lane ID. Type in the number next to the lane ID that you wish to edit. 

You will then be prompted to type a new value that will replace the default lane ID. Hit enter to submit your value.

The `true_id` for key will be updated with your value the menu will cycle again. Continue to select option 1 if you wish to continue renaming the default lane IDs. 

#### Made a mistake? 

No worries, just go to option 1 and select the ID you wish to edit again. 

#### Saving progress

Need to take a break from renaming, no problem. Select option 2 and the function will break and your in-progress-key will be saved in the `naming_lanes` object. 

```{r}
naming_lanes
```


#### Resume progress

If you would like to resume renaming the lane ids, simply provide the `naming_lanes` object into the `assign_subj_ids()` again using the `key` argument. Again, remember to assign the output of the function to an object. In this circumstance, I think its sensible to reassign the function to the same object i.e. `naming_lanes`. 

```{r}
naming_lanes <- assign_subj_ids(renamed_blanks, key = naming_lanes)
```

#### Update rename columns in data

Once you have finished populating the key with your own ids for each lane, selection **option 3**. Remember to assign the output of the function to an object so you can view your updated data.

### Saving output

Check out your output, see if you are happy with it. Then use whatever method you like to save the output. Here we will use `write_csv()`. 

We will also use the `file` object we created earlier to help renaming the output file.
Notice how `file` contains the entire file path?  We just want file name, thats what `extract_file_name(file)` is for. It will pull out the relevant file name without the extension for us. 

```{r}
file_name <- extract_file_name(file)
file_name
```

We will use `paste0()` to concatenate `output/`, the `file_name ` and `_cleaned.csv` to create the file path where your newly cleaned .csv will be saved.

In the example below, the `.csv` will be saved in the `output/`.  Feel free to change the folder and suffix. Make sure that `output/` exists in your project directory.

```{r}
paste0("output/", file_name, "_cleaned.csv")

write_csv(naming_lanes, 
          file = paste0(file_name, "_cleaned.csv"))
```

